\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
FTLR subsubsection updated.

\subsubsection{Fundamental theorem}
With the logical relation defined, we state the fundamental theorem of logical relations (FTLR).
\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  and either $[\baddr,\eaddr] \subseteq \ta$ and $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps or
$[\baddr,\eaddr] \mathrel{\#} \ta$,
then 
  \[
    \npair{\left(((\rx,\normal),\baddr,\eaddr,\aaddr),
      ((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \in \lre(W)
  \]
\end{lemma}
The FTLR roughly says that any executable capability used for execution in a safe environment won't break the capability machine guarantees.
This is, however, only true for syntactically well-formed code, which the $\xReadCond{}$ ensures, and for trusted code the semantic reasonability condition must also be satisfied by the code.
The proof of the FTLR is done by a nested induction that categorises and considers each possible step the two executions can take.
While the lemma is not used directly in the proof sketch we present in Section~\ref{subsec:proof-sketch}, it is detrimental to the proof of the lemmas we use in it.

>>>>

\subsubsection{Fundamental theorem}
With the logical relation defined, we state the fundamental theorem of logical relations (FTLR).
\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  and either $[\baddr,\eaddr] \subseteq \ta$ and $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps or
$[\baddr,\eaddr] \mathrel{\#} \ta$,
then 
  \[
    \npair{\left(((\rx,\normal),\baddr,\eaddr,\aaddr), ((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \in \lre(W)
  \]
\end{lemma}
Roughly speaking, the FTLR says that any executable capability used for execution in a safe environment won't break the capability machine guarantees.
This is, however, only true for syntactically well-formed code, which the $\xReadCond{}$ entails, and for trusted code the semantic reasonability condition must also be satisfied.
The proof of the FTLR is done by a nested induction where each instruction that could be executed is considered.
While the lemma is not directly used in the proof sketch we present in Section~\ref{subsec:proof-sketch}, it is detrimental to the proofs of the lemmas in that section.
